True Lies

### 2018-11-05 GSV-comment-brief.Rmd
Final tweaks

TODO XXX: point out the claims they make.

@@

Lastly, I suggest a simple way to avoid these statistical shenanigans. Ask a group of *N*
experimental subjects, not to flip a coin, but to draw a black or white ball, without replacement,
from an urn containing *N* balls, of which *T* are white. Pay them if they report a white ball. You
will then know -- not estimate -- that the proportion of lies told is $(R - T)/(N - T)$, and this
will also be the proportion of liars, in a sample of exactly $N - T$ subjects. So you can
simultaneously estimate the proportion of lies, and of the lying liars who tell them.

>>>>

@@

Lastly, here is a simple experimental design to avoid these statistical shenanigans. Ask a group of *N*
experimental subjects, not to flip a coin, but to draw a black or white ball, without replacement,
from an urn containing *N* balls, of which *T* are white. Pay them if they report a white ball. You
will then know -- not estimate -- that the proportion of lies told is $(R - T)/(N - T)$, and this
will also be the proportion of liars, in a sample of exactly $N - T$ subjects. You can compare
different samples, or test for no lying, using a straightforward chi-squared test.
So, you can simultaneously estimate the proportion of lies, and of the lying liars who tell them.
